### 2019-08-29 manuscript/manuscript.tex
updated res section

Using the \textcite{Barghi2019-qy} study's data, we used the empirical neutral
null to investigate whether there was a general trend for the temporal
covariance $\cov(\Delta p_t, \Delta p_{t+k})$ to be positive for small $k$ (as
expected under selection), but then become systematically negative for larger
$k$ (as would occur under evolutionary processes that reverse the fitness of
regions across the genome). Such a change in the fitness direction of
haplotypes would not be discernible from genome-wide covariances like those in
Figure \ref{fig:figure-1}. We find (Figure \ref{fig:figure-3} A and B), pooling
across all replicates (see Supplementary Figure
\ref{suppfig:barghi-offset-replicate-panels} for individuals replicates), that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy left tail).

@@

  \caption{A, B: The distribution of temporal covariances calculated in 100kb
    genomic windows from the \textcite{Barghi2019-qy} study, plotted alongside
    an empirical neutral null distribution created by recalculating the
    windowed covariances on sign permuting the allele frequency changes. In
    subfigure A, windowed covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are
    separated by $k=2 \times 10$ generations and in subfigure B the covariances
    are separated by $k=4 \times 10$ generations; each $k$ is an off-diagonal
    from the variance diagonal of the temporal covariance matrix (see cartoon
    of upper-triangle of covariance matrix in subfigures A and B, where the red
    diagonal is the variance, and the dark gray indicates which off-diagonal of
    the covariance matrix is plotted in the histograms). C: The lower and upper
    tail probabilities of the observed windowed covariances, at 20\% and 80\%
    quintiles of the empirical neutral null distribution, for varying time
    between allele frequency changes (i.e. which off-diagonal $k$). The
    confidence intervals are  $95\%$ block-bootstrap confidence interval, and the
    light gray dashed line indicates the 20\% tail probability expected under the
    neutral null.}

>>>>

Using the \textcite{Barghi2019-qy} study's data, we used the empirical neutral
null to investigate whether there was a general trend for the temporal
covariance $\cov(\Delta p_t, \Delta p_{t+k})$ to be positive for small $k$ (as
expected under selection), but then become systematically negative for larger
$k$ (as would occur under evolutionary processes that reverse the fitness of
regions across the genome). Such a change in the fitness direction of
haplotypes would not be discernible from genome-wide covariances like those in
Figure \ref{fig:figure-1}. We find (Figure \ref{fig:figure-3} A and B), pooling
across all replicates (see Supplementary Figure
\ref{suppfig:barghi-offset-replicate-panels} for individuals replicates), that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy left tail).
We additionally quantified the degree to which the left and right tails change
as we look at covariances between timepoints further apart (Figure
\ref{fig:figure-3} C). We find that for covariances 2 timepoints apart ($k=2
\times 10$ generations), the $20\%$ right tail is inflated by a of 1.3 (95\% CI
[1.29, 1.32]), consistent with linked selection creating positive covariance in
allele frequency change. Under constant directional selection, we expect these
positive covariances between increasingly distant timepoints to decay to zero
as additive genetic variance is exhausted by selection and linkage
disequilibrium decays. Instead we find that for covariances 4 timepoints apart
($k=4 \times 10$ generations), the left tail of negative covariances is
inflated by a factor of 1.19 (95\% CI [1.17, 1.21]). Overall, we see a striking
pattern that covariances not only decay towards zero, but in fact become
negative through time, consistent with some regions in the genome having had a
reversed fitness effect at later timepoints.

@@

  \caption{A, B: The distribution of temporal covariances calculated in 100kb
    genomic windows from the \textcite{Barghi2019-qy} study, plotted alongside
    an empirical neutral null distribution created by recalculating the
    windowed covariances on sign permuting the allele frequency changes. In
    subfigure A, windowed covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are
    separated by $k=2 \times 10$ generations and in subfigure B the covariances
    are separated by $k=4 \times 10$ generations; each $k$ is an off-diagonal
    from the variance diagonal of the temporal covariance matrix (see cartoon
    of upper-triangle of covariance matrix in subfigures A and B, where the
    first diagonal is the variance, and the dark gray indicates which
    off-diagonal of the covariance matrix is plotted in the histograms). C: The
    lower and upper tail probabilities of the observed windowed covariances, at
    20\% and 80\% quintiles of the empirical neutral null distribution, for
    varying time between allele frequency changes (i.e. which off-diagonal
    $k$). The confidence intervals are  $95\%$ block-bootstrap confidence
    interval, and the light gray dashed line indicates the 20\% tail
    probability expected under the neutral null.}
